Automatic discovery of cell types and microcircuitry from neural connectomics

### 2014-01-08 docs/paper.tex
oops

The retina of the mouse \autocite{Masland2001} is an example where we
should expect to have connectivity patterns that are well approximated
by our generative model. It is known that there are multiple classes
of cells that can be grouped into ganglion cells that transmit
information to the rest of the brain, bipolar cells that connect
between different cells, and amacrine cells that feed into the
ganglion cells \autocite{cite some review}. Recent research
\autocite{Helmstaedter2013} has produced a large dataset containing
both the types of cells from orthogonal approaches, and also the
connectivity matrix between all reconstructed cells. We want to know
to which level we can classify neurons into types based on this
connectivity only.

@@

To pick the MAP, we run up to $100$ simultaneous chains in parallel,
initialized from different random initial points in the state space,
and then pick the chain with the highest log likelihood. Early
experiments attempted to use the full ensemble of chains as an
estimate of the posterior but were abandoned due to the difficulty of
summarizing the posterior over such a complex state space, which is an
ongoing area of research in the probabilistic modeling community
\todo{cite more? missing}.

>>>>

The retina of the mouse \autocite{Masland2001} is an example where we
should expect to have connectivity patterns that are well approximated
by our generative model. It is known that there are multiple classes
of cells that can be grouped into ganglion cells that transmit
information to the rest of the brain, bipolar cells that connect
between different cells, and amacrine cells that feed into the
ganglion cells. Recent research
\autocite{Helmstaedter2013} has produced a large dataset containing
both the types of cells from orthogonal approaches, and also the
connectivity matrix between all reconstructed cells. We want to know
to which level we can classify neurons into types based on this
connectivity only.

@@

To pick the MAP, we run up to $100$ simultaneous chains in parallel,
initialized from different random initial points in the state space,
and then pick the chain with the highest log likelihood. Early
experiments attempted to use the full ensemble of chains as an
estimate of the posterior but were abandoned due to the difficulty of
summarizing the posterior over such a complex state space, which is an
ongoing area of research in the probabilistic modeling community.
